### 2016-02-19 Projects/DelCo_2014_2015/Reports/Hose_Stream_Report/TeX_Files/DelCo_Hose_Stream_Tests.tex
Edits to hose stream report and figure

% ================
% = Introduction =
% ================
\chapter{Introduction}
\label{chap:intro}
\section{Background}
\label{sec:background}
%More hose stream studies and explanations

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/hose_streams.pdf}
	\caption[Hose stream patterns used in experiments.]{The three types of stream patterns used during water flow experiments. From left to right: straight stream, narrow fog stream, and wide fog stream.}
	\label{fig:hose_streams}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/TJI_support}
	\caption[TJI-constructed ceiling support of the West Structure.]{First floor ceiling support of the West Structure composed of wood truss joist I-beams. View is of the southeast corner of the structure.}
	\label{fig:TJI}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/flow_meter}
	\caption[Flow meter used to measure flow rate during experiments.]{Pressure and flow meter combination used to measure water flow rate during the experiments.}
	\label{fig:flow_meter}
\end{figure}
\FloatBarrier

@@

A total of six test series were conducted to study the impact of different hose stream and application patterns on gas movement in a structure; three test series used a combination nozzle attached to a monitor to flow water and the other three used a combination nozzle attached directly to a hoseline to flow water (Fig.~\ref{fig:monitor+handline}). Experiments that used a monitor to flow water always applied the stream in a fixed position and thus were focused on changing the location of water application in addition to the stream pattern, while the experiments that used a combination nozzle attached directly to a hoseline to flow water focused on varying the pattern in which water was applied in addition to the stream pattern.

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Floor_Plans/Specific_Tests/East_Hose_Test_Annotated}
	\caption[Plan view of the East Structure setup for Tests 33 and 34.]{Plan view of the East Structure setup for Tests 33 and 34. The view is annotated with the approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of BDP A6 (blue square).}
	\label{fig:east_setup}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
	\\~\\
	\includegraphics[width=6in]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_18_1st_Floor_Annotated}
	\caption[Plan view of the West Structure setup for Tests 16 and 18.]{Plan view of the second floor (top) and first floor (bottom) setup in the West Structure for Tests 16 and 18. The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of BDP A10 (blue square). On the second floor, the stairwell door and north side, west double door were opened and closed at certain instances during the tests; the flow path was considered fully established when both doors were in the opened position.}
	\label{fig:flow_path_1}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
	\\~\\
	\includegraphics[width=6in]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_19_1st_Floor_Annotated}
	\caption[Plan view of the West Structure setup for Tests 17 and 19.]{Plan view of the second floor (top) and first floor (bottom) setup in the West Structure for Tests 17 and 19. The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of BDP A10 (blue square). On the second floor, the stairwell door and north side, west double door were opened and closed at certain instances during the tests; the flow path was considered fully established when both doors were in the opened position.}
	\label{fig:flow_path_2}
\end{figure}
\FloatBarrier

@@

% Add flow chart? %
Tests 16 and 17 followed identical procedures that involved using a monitor equipped with a combination nozzle to flow water from the north side double doors of the West Structure to the ceiling of the first floor room. The nozzle was aimed at two targets during the series: a "near" target, located approximately 1.8~m (6~ft) from the interior side of the north wall and a "far" target, located approximately 3.7~m (12~ft) from the interior side of the north wall. The procedure for each test series began by flowing water in a straight stream pattern at the far target for 60 seconds. After 60 seconds of water flow, the stairwell door was opened. One minute later, the west double door on the north side of the second floor was opened, and water continued to flow for 60 seconds. Next, the water flow was stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the near target. The entire process was repeated using the narrow fog and wide fog streams. Fig.~\ref{fig:test_16_17_pic} contains images of each type of hose stream aimed at the near and far targets.

\begin{figure}[!ht]
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/SS_near}
	\end{center} 
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/NF_near}
	\end{center}
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/WF_near}
	\end{center}
	\endminipage \hfill
	\vspace{0.15in}
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/SS_far}
	\end{center} 
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/NF_far}
	\end{center}
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/WF_far}
	\end{center}
	\endminipage \hfill
	\caption[Straight stream, narrow fog stream, and wide fog stream aimed at the near and far targets in the West Structure.]{Straight stream (left column), narrow fog stream (middle column), and wide fog stream (right column) aimed at "near" target (top row) and "far" target (bottom row) during the monitor experiments in the West Structure.}
	\label{fig:test_16_17_pic}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Plots/Test_16_West_063014_BDP_A10_stream_avgs}
	\caption{Average velocity measured by the BDPs at A10 during Test 16 for three hose stream patterns.}
	\label{fig:Test_16_BDP_A10_Avg_All}
\end{figure}
\FloatBarrier

@@

\begin{table}[!ht]
\caption{Average air velocity (m/s $\pm15$\%) through interior doorway when flow path was fully established for each monitor experiment}
\begin{tabular}{lccccc}
\toprule
 & \multicolumn{2}{c}{\underline{Test 16}} & \multicolumn{2}{c}{\underline{Test 17}} & \underline{Test 33}
\\
% \textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} 
\textbf{Stream} & 
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\begin{tabular}{@{}c@{}} \textbf{Room B} \\ \textbf{South Doorway} \\ \end{tabular}
\\ 
\midrule
\textit{Straight} & 0.9 $\pm0.1$ & 0.9 $\pm0.2$ & 0.7 $\pm0.1$ & 0.7 $\pm0.2$ & -0.3 $\pm0.1$
\\ \multicolumn{6}{c}{} \\
\textit{Narrow Fog} & 0.9 $\pm0.2$ & 1.4 $\pm0.2$ & 0.7 $\pm0.2$ & 0.7 $\pm0.1$ & 1.0 $\pm0.6$
\\ \multicolumn{6}{c}{} \\
\textit{Wide Fog} & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.2$ & 2.4 $\pm0.3$
\\ \midrule
 & \multicolumn{2}{c}{\underline{Test 70}} & \multicolumn{3}{c}{} \\
\textbf{Stream} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & 
\begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\multicolumn{3}{c}{} 
\\
\midrule
\textit{Straight} & 1.7 $\pm0.2$ & 1.9 $\pm0.2$ & \multicolumn{3}{c}{} 
\\ \multicolumn{6}{c}{} \\
\textit{Smooth Bore} & 1.7 $\pm0.2$ & 2.0 $\pm0.4$ & \multicolumn{3}{c}{}
\\
\bottomrule
\end{tabular}
\label{table:all_mon_vel_avgs}
\end{table}
\FloatBarrier

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Plots/Test_18_West_063014_BDP_A10_stream_avgs}
	\caption{Average velocity measured by the BDPs at A10 during Test 18 for the three hose stream patterns.}
	\label{fig:Test_18_BDP_A10_Avg_All}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Plots/Test_17_West_063014_BDP_A10_stream_avgs}
	\caption{Average velocity measured by the BDPs at A10 during Test 17 for three hose stream patterns.}
	\label{fig:Test_17_BDP_A10_Avg_All}
	\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Plots/Test_19_West_063014_BDP_A10_stream_avgs}
	\caption{Average velocity measured by the BDPs at A10 during Test 19 for the three hose stream patterns.}
	\label{fig:Test_19_BDP_A10_Avg_All}
\end{figure}

>>>>

% ================
% = Introduction =
% ================
\chapter{Introduction}
\label{chap:intro}
\section{Background}
\label{sec:background}
% More hose stream studies and explanations

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Pictures/hose_streams.pdf}
	\caption[Hose stream patterns used in experiments.]{The three types of stream patterns used during water flow experiments. From left to right: straight stream, narrow fog stream, and wide fog stream.}
	\label{fig:hose_streams}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Pictures/TJI_support}
	\caption[TJI-constructed ceiling support of the West Structure.]{First floor ceiling support of the West Structure composed of wood truss joist I-beams. View is of the southeast corner of the structure.}
	\label{fig:TJI}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Pictures/flow_meter}
	\caption[Flow meter used to measure flow rate during experiments.]{Pressure and flow meter combination used to measure water flow rate during the experiments.}
	\label{fig:flow_meter}
\end{figure}
\FloatBarrier

@@

A total of seven test series were conducted to study the impact of different hose stream and application patterns on gas movement in a structure; three test series used a combination nozzle attached to a monitor to flow water and the other three used a combination nozzle attached directly to a hoseline to flow water (Fig.~\ref{fig:monitor+handline}). Experiments that used a monitor to flow water always applied the stream in a fixed position and thus were focused on changing the location of water application in addition to the stream pattern, while the experiments that used a combination nozzle attached directly to a hoseline to flow water focused on varying the pattern in which water was applied in addition to the stream pattern.

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/East_Hose_Test_Annotated}
	\caption[Plan view of the East Structure setup for Tests 33 and 34.]{Plan view of the East Structure setup for Tests 33 and 34. The view is annotated with the approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of BDP A6 (blue square).}
	\label{fig:east_setup}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
	\\~\\
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_18_1st_Floor_Annotated}
	\caption[Plan view of the West Structure setup for Tests 16 and 18.]{Plan view of the second floor (top) and first floor (bottom) setup in the West Structure for Tests 16 and 18. The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of BDP A10 (blue square). On the second floor, the stairwell door and north side, west double door were opened and closed at certain instances during the tests; the flow path was considered fully established when both doors were in the opened position.}
	\label{fig:flow_path_1}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
	\\~\\
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_19_1st_Floor_Annotated}
	\caption[Plan view of the West Structure setup for Tests 17 and 19.]{Plan view of the second floor (top) and first floor (bottom) setup in the West Structure for Tests 17 and 19. The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of BDP A10 (blue square). On the second floor, the stairwell door and north side, west double door were opened and closed at certain instances during the tests; the flow path was considered fully established when both doors were in the opened position.}
	\label{fig:flow_path_2}
\end{figure}
\FloatBarrier

@@

% Add flow chart? %
Tests 16 and 17 followed identical procedures that involved using a monitor equipped with a combination nozzle to flow water from the north side double doors of the West Structure to the ceiling of the first floor room. The nozzle was aimed at two targets during the series: a ``near" target, located approximately 1.8~m (6~ft) from the interior side of the north wall and a ``far" target, located approximately 3.7~m (12~ft) from the interior side of the north wall. The procedure for each test series began by flowing water in a straight stream pattern at the far target for 60 seconds. After 60 seconds of water flow, the stairwell door was opened. One minute later, the west double door on the north side of the second floor was opened, and water continued to flow for 60 seconds. Next, the water flow was stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the near target. The entire process was repeated using the narrow fog and wide fog streams. Fig.~\ref{fig:test_16_17_pic} contains images of each type of hose stream aimed at the near and far targets.

\begin{figure}[!ht]
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/SS_near}
	\end{center} 
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/NF_near}
	\end{center}
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/WF_near}
	\end{center}
	\endminipage \hfill
	\vspace{0.15in}
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/SS_far}
	\end{center} 
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/NF_far}
	\end{center}
	\endminipage \hfill
	\minipage{2.15in}
	\begin{center}
		\includegraphics[width=2in]{../Figures/Pictures/WF_far}
	\end{center}
	\endminipage \hfill
	\caption[Straight stream, narrow fog stream, and wide fog stream aimed at the near and far targets in the West Structure.]{Straight stream (left column), narrow fog stream (middle column), and wide fog stream (right column) aimed at ``near" target (top row) and ``far" target (bottom row) during the monitor experiments in the West Structure.}
	\label{fig:test_16_17_pic}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_16_West_063014_BDP_A10_stream_avgs}
	\caption{Average velocity measured by the BDPs at A10 during Test 16 for three hose stream patterns.}
	\label{fig:Test_16_BDP_A10_Avg_All}
\end{figure}
\FloatBarrier

@@

\begin{table}[!ht]
\caption{Average air velocity (m/s) through interior doorway when flow path was fully established for each monitor experiment}
\begin{tabular}{lccccc}
\toprule
 & \multicolumn{2}{c}{\underline{Test 16}} & \multicolumn{2}{c}{\underline{Test 17}} & \underline{Test 33}
\\
% \textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} 
\textbf{Stream} & 
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\begin{tabular}{@{}c@{}} \textbf{Room B} \\ \textbf{South Doorway} \\ \end{tabular}
\\ 
\midrule
\textit{Straight} & 0.9 $\pm0.1$ & 0.9 $\pm0.2$ & 0.7 $\pm0.1$ & 0.7 $\pm0.2$ & -0.3 $\pm0.1$
\\ \multicolumn{6}{c}{} \\
\textit{Narrow Fog} & 0.9 $\pm0.2$ & 1.4 $\pm0.2$ & 0.7 $\pm0.2$ & 0.7 $\pm0.1$ & 1.0 $\pm0.6$
\\ \multicolumn{6}{c}{} \\
\textit{Wide Fog} & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.2$ & 2.4 $\pm0.3$
\\ \midrule
 & \multicolumn{2}{c}{\underline{Test 70}} & \multicolumn{3}{c}{} \\
\textbf{Stream} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & 
\begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\multicolumn{3}{c}{} 
\\
\midrule
\textit{Straight} & 1.7 $\pm0.4$ & 1.9 $\pm0.5$ & \multicolumn{3}{c}{} 
\\ \multicolumn{6}{c}{} \\
\textit{Smooth Bore} & 1.7 $\pm0.5$ & 2.0 $\pm0.5$ & \multicolumn{3}{c}{}
\\
\bottomrule
\end{tabular}
\label{table:all_mon_vel_avgs}
\end{table}
\FloatBarrier

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_18_West_063014_BDP_A10_stream_avgs}
	\caption{Average velocity measured by the BDPs at A10 during Test 18 for the three hose stream patterns.}
	\label{fig:Test_18_BDP_A10_Avg_All}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_17_West_063014_BDP_A10_stream_avgs}
	\caption{Average velocity measured by the BDPs at A10 during Test 17 for three hose stream patterns.}
	\label{fig:Test_17_BDP_A10_Avg_All}
	\end{figure}
\FloatBarrier

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_70_West_101215_BDP_A10_stream_avgs}
	\caption{Average velocity measured by the BDPs at A10 during Test 70 for straight stream and smooth bore stream patterns.}
	\label{fig:Test_70_BDP_A10_Avg_All}
	\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_19_West_063014_BDP_A10_stream_avgs}
	\caption{Average velocity measured by the BDPs at A10 during Test 19 for the three hose stream patterns.}
	\label{fig:Test_19_BDP_A10_Avg_All}
\end{figure}
